Critical Temperature of YBCO and BSCCO Superconductors

### 2014-12-13 Draft.tex
added average comment
edit values

Superconductors are materials that lose their electrical resistance when they fall below a certain temperature, called the critical temperature. We determined the critical temperatures for $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ to be $98.35\textrm{ K} \pm 7\textrm{ K}$. We found a single phase transition at $110\text{ K}\pm 9 \text{ K}$ for $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$ as well.
The critical temperatures are found by passing a fixed current through a superconducting sample and measuring the change in voltage across the sample to determine its resistance. We describe the critical temperature as the temperature halfway through the transition from non-zero resistance to zero resistance. 
Previous measurement of the critical temperature for YBCO gives a critical temperature of 91 K. Our critical temperature for BSCCO is in agreement with previous measurements for $n=3$ phase found in the literature. 
This confirms that our BSCCO consists of mainly $n=3$, as indicated in the manual that came with our samples. 
We also saw agreement with a general decrease in critical temperature with an increase in current run through the YBCO sample, however the transition was uneven and distorted, so a specific difference in critical temperature could not be determined.

@@

\begin{figure}[hb!]
\centering
\includegraphics[width=7in]{ybco_sand_warmup_116_resistance_vs_temp.png}
\caption{Plot of resistance vs temperature for YBCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between. Data was gathered every 20 seconds during warm-up.}
\label{YBCOplot1}
\end{figure}

\begin{figure}[hb!]
\centering
\includegraphics[width=7in]{ybco_sand_warmup_1111_resistance_vs_temp.png}
\caption{Plot of resistance vs temperature for YBCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between. Data was gathered every 30 seconds until onset of superconductivity, then every couple seconds throughout the transition period.}
\label{YBCOplot2}
\end{figure}

\begin{figure}[hb!]
\centering
\includegraphics[width=7in]{100ma_current_ybco_critical_temperature}
\caption{Plot of resistor voltage vs temperature for a current of 100mA during transition from superconducting to non-superconducting.}
\label{100mA}
\end{figure}

@@

Superconductivity was clearly achieved in both the YBCO and the BSCCO samples, and their transition to being non-superconductive as their temperature increased was recorded. Graphical analysis yielded a critical temperature for YBCO of 98.35K $\pm$ 7K and for BSCCO of 110K $\pm$ 9K. According to the Colorado Superconductor Inc manual, YBCO has a critical temperature of 92K, which is within our margin of error; similarly, the BSCCO sample was noted as having a critical temperature of 105K, again within our margin of error. The strange behavior seen during the end of the superconducting phase of the BSCCO sample may also have had to do with the fact that BSCCO can have two other critical temperatures. The general formula is $\text{Bi}_{2,1}\text{Sr}_{n+1}\text{Ca}_{\text{n}-1}\text{Cu}_{\text{n}}\text{O}_{2n+4+\delta}$. While the sample we had was specified for $n=3$, it is quite possible that other variations were present in our sample, each with their own critical temperature: $T_C$ for $n=1$ is 80K and $T_C$ for $n=2$ is 90K. \cite{colo} While we did not get as cold as 80K, we could be seeing some sections stop superconducting around 90K, alongside the already non-superconducting $n=1$ material, giving us a not truly flat superconducting zone. Finally, looking at the transition for YBCO with a current of 100mA, despite problems identifying a strict number for the critical temperature, the transition to non-superconducting clearly happens at a lower temperature then for 1mA. This is consistent with expectations since more energy from the increased current means that less thermal energy from warming up is needed to impart enough energy to stop the superconducting state within the YBCO crystals.

>>>>

Superconductors are materials that lose their electrical resistance when they fall below a certain temperature, called the critical temperature. We determined the critical temperatures for $\text{Yt}\text{Ba}_{2}\text{Cu}_{3}\text{O}_{7-\delta}$ to be $98 \pm 7\textrm{ K}$. We found a single phase transition at $110 \pm 9 \text{ K}$ for $\text{Bi}_{2}\text{Sr}_{2}\text{Ca}_{n-1}\text{Cu}_{n}\text{O}_{2n+4}$ as well.
The critical temperatures are found by passing a fixed current through a superconducting sample and measuring the change in voltage across the sample to determine its resistance. We describe the critical temperature as the temperature halfway through the transition from non-zero resistance to zero resistance. 
Previous measurement of the critical temperature for YBCO from literature gives a critical temperature of 91 K. THe manual that came with our sample indicates a critical temperature of $92$ for $YBCO$. Both of these agree with the range we determined for the critical temperature.
Our critical temperature for BSCCO is in agreement with previous measurements for $n=3$ phase found in the literature. 
This confirms that our BSCCO consists of mainly $n=3$, as indicated in the manual. 
We also saw agreement with a general decrease in critical temperature with an increase in current run through the YBCO sample, however the transition was uneven and distorted, so a specific difference in critical temperature could not be determined.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=7in]{ybco_sand_warmup_116_resistance_vs_temp.png}
\caption{Plot of resistance vs temperature for YBCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between. Data was gathered every 20 seconds during warm-up.}
\label{YBCOplot1}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=7in]{ybco_sand_warmup_1111_resistance_vs_temp.png}
\caption{Plot of resistance vs temperature for YBCO sample, with best fit lines during normal conductivity and during superconductivity, with a third line showing the space equidistant between. Data was gathered every 30 seconds until onset of superconductivity, then every couple seconds throughout the transition period.}
\label{YBCOplot2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=7in]{100ma_current_ybco_critical_temperature}
\caption{Plot of resistor voltage vs temperature for a current of 100mA during transition from superconducting to non-superconducting.}
\label{100mA}
\end{figure}

@@

Superconductivity was clearly achieved in both the YBCO and the BSCCO samples, and their transition to being non-superconductive as their temperature increased was recorded. Graphical analysis yielded a critical temperature for YBCO of 98 $\pm$ 7K and for BSCCO of 110K $\pm$ 9K. 
According to the Colorado Superconductor Inc manual, YBCO has a critical temperature of 92K, which is within our margin of error; similarly, the BSCCO sample was noted as having a critical temperature of 105K, again within our margin of error. 
The strange behavior seen during the end of the superconducting phase of the BSCCO sample may also have had to do with the fact that BSCCO can have two other critical temperatures. The general formula is $\text{Bi}_{2,1}\text{Sr}_{n+1}\text{Ca}_{\text{n}-1}\text{Cu}_{\text{n}}\text{O}_{2n+4+\delta}$. 
While the sample we had was specified for $n=3$, it is quite possible that $n=2$,  with a $T_C$ of 85K, were also present in our sample. \cite{colo} The fluctuations shown in Fig. \ref{BSCCOplot2} could be due to the $n=2$ compound, which stopped superconducting before the $n=3$ transition. Finally, looking at the transition for YBCO with a current of 100mA, despite problems identifying a strict number for the critical temperature, the transition to non-superconducting clearly happens at a lower temperature then for 1mA. 
This is consistent with expectations since more energy from the increased current means that less thermal energy from warming up is needed to impart enough energy to stop the superconducting state within the YBCO crystals.
